### 2011-02-10 paper/results.tex
Fixed ref

Before optimizing the chosen family of
parameterized gaits (\secref{motionModel}) with learning methods, we performed an experiment to explore the five dimensions of the parameter space. Specifically, we first selected a random parameter vector that resulted
in motion, but not an exceptional gait. In five different experiments, we then varied each parameter
individually and measured performance.
Each measurement was repeated to get a rough estimate
of the measurement noise at each point.  The results
of this exploration (Figures \ref{fig:explore_dim_1} through
\ref{fig:explore_dim_5}) reveal that some dimensions
are smoother than others and that the measurement noise is variable and can be quite high.

>>>>

Before optimizing the chosen family of parameterized gaits
(\secref{motionModel}) with learning methods, we performed an
experiment to explore the five dimensions of the parameter
space. Specifically, we first selected a random parameter vector that
resulted in motion, but not an exceptional gait. In five different
experiments, we then varied each parameter individually and measured
performance.  Each measurement was repeated to get a rough estimate of
the measurement noise at each point.  The results of this exploration
(\figref{explore_dim_1}) reveal that some dimensions are smoother than
others and that the measurement noise is variable and can be quite
high.
